---
title: "MS_Method"
author: "Matthew Hamilton"
date: "13/10/2020"
output:
  bookdown::pdf_document2: default
  html_document: default
  pdf_document: default
---
## Sample and setting
`r results_ls$study_descs_ls$sample_desc_1L_chr`

## Measures
Data was collected on utility weights, `r get_nbr_of_predrs(results_ls)` candidate predictors of utility weights and descriptive population characteristics. 

### Utility weights
Utility weights were assessed using the `r get_hlth_utl_nm(results_ls)` multi-attribute utility instrument.

### Candidate predictor`r ifelse(get_nbr_of_predrs(results_ls, as_words_1L_lgl = F)>1,"s","")`
`r make_cndt_predr_text(results_ls)` 

`r get_predrs_by_ctg(results_ls, long_desc_1L_lgl = T) %>% paste0(collapse=" ")`

### Population characteristics
Population characteristic data were `r get_popl_descvs(results_ls) %>% sort()`.

## Statistical analysis
We implemented the generalised form of the study analysis algorithm developed by Hamilton, Gao and colleagues [@HamiltonGao2021], the key steps of which are summarised as follows.

### Descriptive statistics
Basic descriptive statistics were used to characterise the cohort in terms of baseline population variables. Pearson’s Product Moment Correlations (*r*) were used to determine the relationships between candidate predictors and the `r get_hlth_utl_nm(results_ls)` utility score.

### Model evaluation 
We compared predictive performance of a range of models predicting `r get_hlth_utl_nm(results_ls)` utility scores using the candidate predictor that had the highest Pearson correlation coefficient with utility scores. The models compared include `r get_mdl_cmprsns(results_ls, describe_1L_lgl = F)`. `r get_mdl_cmprsns(results_ls)`. Ten-fold cross-validation was used to compare model fitting with training datasets and predictive ability with testing datasets using three indicators including R^2^, root mean square error (RMSE) and mean absolute error (MAE)  [@RN20; @RN19].

To evaluate whether candidate predictors could independently predict utility scores, we established multivariate prediction models using baseline data with the candidate predictor and `r get_covar_ctgs(results_ls)` covariates. `r get_covars_by_ctg(results_ls, collapse_1L_lgl = T) %>% paste0(collapse = " ")`

`r ifelse(get_nbr_of_predrs(results_ls, as_words_1L_lgl = F)>1,"### Candidate predictor comparison","")`
`r make_cndt_predr_text(results_ls, type = "comparison")` 

### Utility mapping models
We next established models using `r get_mdl_cmprsns(results_ls, describe_1L_lgl = F, mixed_1L_lgl = T)` `r ifelse(is.na(results_ls$cohort_ls$n_fup_1L_dbl),""," that included both the baseline and follow-up data")`. Model fitting was evaluated using Bayesian R^2^ [@RN21].
```{r echo=FALSE}
if(!is.na(results_ls$cohort_ls$n_fup_1L_dbl)){
  assessing_change_1L_chr <- c("../Child_RMDs/MS_Method_change.Rmd")
}else{
  assessing_change_1L_chr <- NULL
}
```
```{r child=assessing_change_1L_chr, echo=FALSE, warning=FALSE}
```

### Software
We undertook all our analyses using  `r X@b_SpecificResults@a_SpecificShareable@shareable_outp_ls$session_ls$R.version$version.string %>% stringr::str_sub(end=-14)` [@RCitation] using the TTU package [@TTUPackage] (version `r X@b_SpecificResults@a_SpecificShareable@shareable_outp_ls$session_ls$otherPkgs$TTU$Version`). 
