---
title: "Longitudinal TTU"
author: "Matthew Hamilton"
date: "26/01/2021"
output: html_document
---

## Longitudinal TTU regression models

<!-- Table start -->Regression coefficients of the baseline score and score changes (from baseline to follow-up) estimated in individual `r get_lngl_ttu_types(results_ls)` models are summarised in `r ifelse(params$output_type_1L_chr=="Word","","Table")` \@ref(tab:cfscl).<!-- Table end --> Bayesian R^2^ and modelled residual standard deviations (SDs) from each model are reported. `r  make_lngl_ttu_r2_text(results_ls, part_int = 1:2)`

`r if(is.null(child_docs_ls$Long_TTU_Coefs)){"(Insert \\@ref(tab:cfscl) about here)"}`
```{r, child = child_docs_ls$Long_TTU_Coefs, echo=FALSE}
```

The mean ratio between the within-person and between-person associated coefficients (${\beta}_{change}/{\beta}_{baseline}$) is `r make_within_between_ratios_text(results_ls)`. 

<!-- Figure start -->Distribution of observed and predicted utility scores and their association from `r results_ls$ttu_lngl_ls$best_mdls_tb %>% purrr::pmap_chr(~paste0(..1," (",..2,")"))  %>% paste0(collapse = ", ") %>% stringi::stri_replace_last(fixed = ",", " and")` using `r results_ls$predr_var_nms_chr %>% paste0(collapse = ", ") %>% stringi::stri_replace_last(fixed = ",", " and")` are plotted in Figure \@ref(fig:fig2)<!-- Figure end -->. <!-- Author judgment start -->

`r make_lngl_ttu_with_covars_text(results_ls)` <!-- Table start --><!-- Comment - need to make the following tables conditional on covariates being evaluated -->(see `r ifelse(params$output_type_1L_chr=="Word","","Tables")` \@ref(tab:coefslongtb) and \@ref(tab:coefsglmtb))<!-- Table end -->. 

<!-- Author judgment start --> `r ifelse(is.null(results_ls$secondary_chr),"",results_ls$secondary_chr[2])` 
Detailed summaries of all models are available in the online data repository (see "Availability of data and materials").
<!-- Author judgment end --> 

<!-- Author judgment end -->

`r if(is.null(child_figs_ls$fig2)){"(Insert Figure \\@ref(fig:fig2) about here)"}`
```{r, child = child_figs_ls$fig2, echo=FALSE}
```
